The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-20 paper/sections/methods.tex
working on shape matching bit

\section{Overview}
The input to the Shape Matching Element Method (SEM)  is a NURBS \emph{boundary representation} of a volumetric object, along with a set of physical parameters 
(density, constitutive model, model parameters etc). The output is an elastodynamic simulation. 
SEM consists of preprocessing and runtime simulation phases~\refalg{sem} and at no point do we need to generate a volumetric mesh of the input. 
In the \emph{preprocessing} stage we use raycasting to find quadrature points and weights for volumetric integration, as well as to compute part blending parameters. 
Finally we construct local shape matching operators and construct the mass matrix for our problem.

@@

\subsection{Shape Matching}
\dave{Shape Matching to a single NURBS part}
In typical FEM in graphics, we make use of tetrahedral or triangular elements with a piecewise-linear function space. In such a case our functions may be evaluated as a weighted combination of the nodal values of an element: $f(\mathbf x)=\sum_{i=0}^n f_i \phi_i(\mathbf{x})$ where $n$ is the number of nodal values and $\phi_i$ is the i-th barycentric coordinates. Thus in this case we have the simple deformation map $\mathbf{x(X)} = \sum_{i=0}^n \mathbf{x}_i \phi_i(\mathbf{X})$. However, our method contrasts this typical approach in that our elements are more general and take the form of any arbitrary boundary primitive, such as NURBS, and also that the function space in non-linear.

>>>>

\section{Overview}
The input to the Shape Matching Element Method (SEM)  is a NURBS \emph{boundary representation} of a volumetric object, along with a set of physical parameters 
(density, constitutive model, model parameters etc). 
The boundary representation is composed of one or more (not necessarily explicit;y connected) NURBS surface primitives that we will call \emph{parts}.
The output is an elastodynamic simulation. 
SEM consists of preprocessing and runtime simulation phases~\refalg{sem} and at no point do we need to generate a volumetric mesh of the input. 
In the \emph{preprocessing} stage we use raycasting to find quadrature points and weights for volumetric integration, as well as to compute part blending parameters. 
Finally we construct local shape matching operators and construct the mass matrix for our problem.

@@

\subsection{Shape Matching}

We begin by describing shape matching to a single NURBS part. 
Given a two different configurations of the same part (specified by the control points), shape matching computes a polynomial deformation which best aligns them.

Let $\vc{q^0}$ be the initial control points of the part, provided by the modeller and Let $\vc{q}$ be a vector of modified control point values.
We can compute the undeformed (or reference) position of any point on our part using $\refX\left(u,v\right) = \Jnurbs\left(u,v\right)\mathbf{q^0}$ and the corresponding
deformed (world space) position as $\defX\left(u,v\right) = \Jnurbs\left(u,v\right)\mathbf{q}$.

We can define a polynomial deformation from $\refX = \begin{pmatrix} X & Y & Z \end{pmatrix}^T$ to $\defX$  as 
\begin{equation}
    \defX\left(\refX\right) = 
    \underbrace{\begin{pmatrix}
    \mathbf{p}^T(\refX-\bar{\refX}) & \mathbf{0} & \mathbf{0} & 1 & 0 & 0\\
    \mathbf{0} & \mathbf{p}^T(\refX-\bar{\refX}) & \mathbf{0} & 0 & 1 & 0\\
    \mathbf{0} & \mathbf{0} & \mathbf{p}^T(\refX-\bar{\refX}) & 0 & 0 & 1\\
    \end{pmatrix}}_{\Pmatx}
    \Pcox,
\end{equation} where $\mathbf{p}^T\left(\refX\right)$ is the polynomial basis vector \newline (eg $\begin{pmatrix} X & Y & X\cdot Y & X\cdot X & Y\cdot Y \end{pmatrix}$ ),
$\bar{\refX}$ is an a priori chosen origin around which to deform, $\Pco$ are the coefficients for the 
non-constant part of the polynomial and $\tr$ is the translation of the deformation origin. 
We can compute the shape matching deformation by solving
\begin{equation}
    \begin{pmatrix} 
        \Pco\\
        \tr
    \end{pmatrix}^* = \arg\min_{\Pco,\tr} \int_{u,v} \left\lvert\left\lvert\Pmatx\Pcox - \refX\right\rvert\right\rvert^2_2 du\cdot dv,
\end{equation} where we have surpressed the dependence of $\refX$ on $u$ and $v$ for the sake of brevity.

Discretizing this integral and solving

\dave{Ty how do we pick u,vs and weights for this formula?}

%%%%% OLD STUFF BELOW HERE %%%%%%%
\dave{Shape Matching to a single NURBS part}
In typical FEM in graphics, we make use of tetrahedral or triangular elements with a piecewise-linear function space. In such a case our functions may be evaluated as a weighted combination of the nodal values of an element: $f(\mathbf x)=\sum_{i=0}^n f_i \phi_i(\mathbf{x})$ where $n$ is the number of nodal values and $\phi_i$ is the i-th barycentric coordinates. Thus in this case we have the simple deformation map $\mathbf{x(X)} = \sum_{i=0}^n \mathbf{x}_i \phi_i(\mathbf{X})$. However, our method contrasts this typical approach in that our elements are more general and take the form of any arbitrary boundary primitive, such as NURBS, and also that the function space in non-linear.
